### 2014-03-15 src/discussion.Rnw
Obeying space requirements (10 pages without reference)

For line count strategies, only the external sampling produced
consistent results, which were again not as good as \textit{round(x)}
for similar mutation reduction ratios. Secondly, we had hypothesised
that perhaps coverage was a significant contributor to having a high
correlation with the full mutation score. However we could find no
evidence in support of this hypothesis with line, method, class, and
project scope showing similar correlation and consistency at similar
reduction ratios.

@@

While the x\% per operator strategy produced consistent results, its
consistency was not as good as \textit{sample(x)}, and was either on
par with or worse than \textit{sample(x)} in correlation.

Considering mutation operators, only three operators \textit{NC},
\textit{RC},and \textit{DC} had consistent results (and only for
original test suites). The n-selection strategy had high correlation and
consistency (though low reduction ratio) until 7-selection (removing
the seven most numerous operators) for both generated and original
test suites.  Javalanche did not have a high mutation reduction ratio,
though it had high correlation for both kinds of test suites. The other
operator selection methods performed poorly on generated test suites,
while they had high correlation and reasonable stability on original test
suites. However, for comparable mutation reduction levels, they all performed
worse than random sampling strategies.

@@

The second pattern is that fractional sampling based on projects
appears to be better than that based on classes, which in turn is
better than methods and lines, with regard to the stability of the
result (i.e. low standard deviation).  This is not clear at lower
levels of reduction (more than 1/32), but becomes more pronounced as
the denominator of the mutant reduction fraction increases.  There
seems to exist a hierarchy of sampling, whereby as sampling becomes
more fine grained stability decreases.  We did not observe the pattern
found by Zhang et al.~\cite{zhang2013ase} where method-based sampling
had the best correlations. In fact, in our measurements, the opposite
may be true, with project based sampling having the highest
correlation with the total mutation score a majority of the time.

>>>>

For line count strategies, only the external sampling produced
consistent results, which were again not as good as \textit{round(x)}
for similar reduction ratios. Secondly, we had hypothesised
that coverage was a significant contributor to having a high
correlation with the full mutation score. However we could find no
evidence in support of this hypothesis with line, method, class, and
project scope showing similar correlation and consistency at similar
reduction ratios.

@@

While the x\% per operator strategy produced consistent results, its
consistency was not as good as \textit{sample(x)}, and was either on
par with or worse than \textit{sample(x)} in $R^2$.

Considering mutation operators, only three operators \textit{NC},
\textit{RC},and \textit{DC} had consistent results (and only for
original test suites). The n-selection strategy had high correlation and
consistency (though low reduction ratio) until 7-selection (removing
the seven most numerous operators) for both generated and original
test suites.  Javalanche did not have a high mutation reduction ratio,
though it had high $R^2$ for both kinds of test suites. The other
operator selection methods performed poorly on generated test suites,
while they had high correlation and reasonable stability on original test
suites. However, for comparable mutation reduction levels, they all performed
worse than random sampling strategies.

@@

The second pattern is that fractional sampling based on projects
appears to be better than that based on classes, which in turn is
better than methods and lines, with regard to the stability of the
result (i.e. low standard deviation).  This is not clear at lower
levels of reduction ($< 1/32$), but becomes more pronounced for lower
ratios. There seems to exist a hierarchy of sampling, whereby as sampling becomes
more fine grained stability decreases.  We did not observe the pattern
found by Zhang et al.~\cite{zhang2013ase} where method-based sampling
had the best correlations. In fact, in our measurements, the opposite
may be true, with project based sampling having the highest
$R^2$ a majority of the time.

### 2014-03-15 src/introduction.Rnw
Obeying space requirements (10 pages without reference)

One of the impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, which renders mutation
analysis prohibitively time consuming.

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.  As an
example, recent work suggests that using statement deletion only can
provide effective mutation analysis~\cite{untch2009onreduced}.

@@

One note about our, and other researchers, evaluation criteria is in
order.  We, like others, use the ability of a sample to correlate well
to the score over all mutants as a measure of sampling quality.  The
underlying reason for this is that, while many mutants have little
ability to distinguish between good and bad test suites, some smaller
set of mutants show subtle deficiencies in suites that are not clear
from, say, code coverage.  The full set of mutants obviously contains
these mutants, and correlating with (rather than exactly matching) the
full mutation score is a strong indicator that many of these
discriminatory mutants have been preserved in a sample.

@@

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation) with the full mutation score, expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies that have not been
previously considered.

\item Our recommendations are useful for both testing researchers who
might be comparing automatically generated test suites, and software
testers in real world development working to produce and evaluate manual test suites.

@@

Our data is available for replication~\cite{data}\footnote{Available on publication}.

>>>>

One of the impediments to wider adoption of mutation analysis is its
high computational cost.  The set of simple mutants for even a
moderate sized program can be very large, making mutation
analysis prohibitivey time consuming.

@@

Selective mutation strategies attempt to select a representative
subset of mutation \emph{operators} based on heuristics and
statistical analysis, and apply this subset of operators to generate
mutants instead of applying the whole set of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.
Recent work suggests that using statement deletion only can
be effective~\cite{untch2009onreduced}.

@@

One note about our, and other researchers, evaluation criteria is in
order.  We, like others, use the ability of a sample to correlate well
to the score over all mutants as a measure of sampling quality.  The
underlying reason for this is that, while many mutants have little
ability to distinguish between good and bad test suites, some smaller
set of mutants show subtle deficiencies in suites that are not clear
from, say, code coverage.  The full set of mutants obviously contains
these mutants, and correlating with (rather than matching) the
full mutation score is a strong indicator that many of these
discriminatory mutants have been preserved in a sample.

@@

\item We compare a much large number of mutant reduction strategies
than previous studies. We compare with respect to the predictive power
(correlation) with the full mutation score, expected mutant reduction,
and the stability of the amount of mutant reduction expected. Our
sampling strategies include some that were suggested by other
researchers, as well as a few novel strategies not previously considered.

\item Our recommendations are useful for both testing researchers who
might be comparing automatically generated test suites, and software
testers in real world working to produce and evaluate manual test suites.

@@

Our data will be available for replication on publication~\cite{data}
%\footnote{Available on publication}.

### 2014-03-15 src/methodology.Rnw
Obeying space requirements (10 pages without reference)

When the number of mutants to be chosen was not a whole number, we used
the formula suggested by Zhang et a.~\cite{zhang2013ase}, and used the
decimal part to select a mutant with that probability.

@@

For the first variant, we applied the x\% sampling to the result of
the first sampling based on line counts. That is, in the case of
methods, we first selected \textit{linecount} mutants each from each
method, and applied the x\% selection to the result of this
selection. For example, for $1/2$ sampling on methods if one method had
$10$ lines and another had $20$ lines, we sampled $10$ mutants from
the first, and $20$ mutants from the second, and from the combined
$30$ mutants, we sampled $15$.  For the second variant, we did the
sampling in one go, where we chose \textit{linecount/x} number of
mutants from each program element.  That is, in the previous example,
only $5$ mutants from the first and $10$ mutants from the second
method would be chosen.

@@

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
\subsubsection{Criteria IV}
Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some were not available in PIT (e.g. IndVarBitNeg).
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
are discarded at each step.

>>>>

When the number of mutants sampled was not a whole number, we used
the formula by Zhang et a.~\cite{zhang2013ase}, using the
decimal part to select a mutant with that probability.

@@

For the first variant, we applied the x\% sampling to the result of
the first sampling based on line counts. That is, in the case of
methods, we first selected \textit{linecount} mutants each from each
method, and applied the x\% selection to this result.
For example, for $1/2$ sampling on methods if one method had
$10$ lines and another had $20$, we sampled $10$ mutants from
the first, and $20$ from the second, and from the combined
$30$ mutants, we sampled $15$.  For the second variant, we did the
sampling in one go, where we chose \textit{linecount/x} number of
mutants from each program element.  That is, in the previous example,
only $5$ mutants from the first and $10$ mutants from the second
method would be chosen.

@@

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
\subsubsection{Criteria IV}
Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some not in PIT.
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
are discarded at each step.

### 2014-03-15 src/related.Rnw
updates: methodology related
For related: got the message, for methodology, fixed
the problems pointed out.
Obeying space requirements (10 pages without reference)

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, or \textit{faster}.
The fewer approaches includes selective mutation and mutant sampling;
weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching techniques, and byte code based mutation analysis systems like PIT.

The idea of using a subset of mutants was conceived along with
mutation analysis itself. Budd~\cite{budd1980mutation} and
Acree~\cite{Acree1980} showed that even 10\% sampling can achieve 99\%
accuracy for the final score.  The idea was further investigated by
Mathur~\cite{mathur1991performance}, Wong et
al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
mutation operators for
Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
suggested constrained mutation where only two mutation operators
were used.%, which were felt to be better than using the entire set.

@@

Zhang et al.~\cite{zhang2010operator} compares operators based mutant
selection techniques proposed in a set of
papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
to random mutant sampling.  They find that none of the selection
techniques are superior to random sampling, with the same number of
mutants. They also find that equal mutation sampling is more effective
for larger subjects compared to equal mutagen sampling and the reverse
is true for smaller subjects. {\bf ADG:  not having defined mutagen/mtuation sampling this is not easy for most readers to understand.  also we switch between "sampling" and "random selection" a lot, I tried to make consistent.}

>>>>

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, or \textit{faster}.
The fewer approaches includes selective mutation and mutant sampling;
weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching etc.

The idea of using a subset of mutants was conceived along with
mutation analysis itself. Budd~\cite{budd1980mutation} and
Acree~\cite{Acree1980} showed that even 10\% sampling can achieve 99\%
accuracy for the final score.  The idea was further investigated by
Mathur~\cite{mathur1991performance}, Wong et
al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
mutation operators for
Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
suggested constrained mutation where only two operators
were used.%, which were felt to be better than using the entire set.

@@

Zhang et al.~\cite{zhang2010operator} compares operators based mutant
selection techniques proposed in a set of
papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
to random mutant sampling.  They find that none of the selection
techniques are superior to random sampling, with the same number of
mutants. They also find that equal mutation sampling is more effective
for larger subjects compared to equal mutagen sampling and the reverse
is true for smaller subjects.
% {\bf ADG:  not having defined mutagen/mtuation sampling this is not easy
% for most readers to understand.  also we switch between "sampling" and
% "random selection" a lot, I tried to make consistent.  }
% RG: Got it.

### 2014-03-15 src/results.Rnw
Obeying space requirements (10 pages without reference)

Finally, Table~\ref{tbl:operators} contains the results when only a single operator
is used, and Table~\ref{tbl:opsel} contains the results for specific operator
selection criteria. The first columns in these two tables contain the particular
operator or operator selection applied. The second column contains the
correlation coefficient $R^2$ with the final mutation score. The third column contains
the mean mutant reduction ratio, and the fourth contains the standard deviation of the
mutant reduction ratio achieved. The fifth column contains the number of projects
that returned valid values for that operator selection mechanism, and the final
column gives the multiplier factor.
The TSDL row is the result of applying only the higher order mutant
equivalent to \textit{statement deletion}.
All the \textit{N-sel} rows are the results of N-selective operator selection
strategies~\cite{offutt1993anexperimental}. We used the order of operators
determined from Figure~\ref{fig:op} for this purpose. The complete data
(only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.

>>>>

Finally, Table~\ref{tbl:operators} contains the results when only a single operator
is used, and Table~\ref{tbl:opsel} contains the results for specific operator
selection criteria. The first columns in these two tables contain the particular
operator or operator selection applied. The second column contains the
coefficient $R^2$ with the final mutation score. The third column contains
the mean mutant reduction ratio, and the fourth contains the standard deviation of the
mutant reduction ratio achieved. The fifth column contains the number of projects
that returned valid values for that operator selection mechanism, and the final
column gives the multiplier factor.
The TSDL row is the result of applying only the higher order mutant
equivalent to \textit{statement deletion}.
All the \textit{N-sel} rows are the results of N-selective operator selection
strategies~\cite{offutt1993anexperimental}, using the order of operators
from Figure~\ref{fig:op}. The complete data
(only for original test suites) is visualized in Figure~\ref{fig:fullimgsize}.

### 2014-03-15 src/threats.Rnw
Obeying space requirements (10 pages without reference)

\section{Threats to Validity}
While we have taken every care to ensure that our results are valid, and to eliminate the
effects of random noise in experiments, our results are subject to the following threats
to validity.

>>>>

\section{Threats to Validity}
While we have taken every care to ensure that our results are valid, and to eliminate the
effects of random noise, our results are subject to the following threats
to validity.
